Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-08-30 Methods.tex
Appendix
Tables, switched to input rather than include
Because nesting

\begin{table}[h!]
\center
\begin{tabular} {|l | l | c|}
\hline
Name & Description & Value \\ \hline
\(n_{w}\) & Number of women & 1000 \\ \hline
\(n_{m}\) & Number of midwives & 100 \\ \hline
\(r_{m}\) & Number of appointments per midwive & 1000 \\ \hline
\(r_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
Runs & Simulation runs & 1000 \\ \hline
\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(q_{w}\) & Probability of women sharing & 0. \\ \hline
\(w_{w}\) & Weight of shared information for women & 0. \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 10:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}

@@

Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of inputs given in table \ref{tab:sa_params}, giving 10 free parameters which were treated as uniformly distrubuted in the range given. Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters. Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out. A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.

To better capture the response characteristics for the model, we measure four outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the interquartile range of the average signal, and interquartile range between simulation runs. Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability in the system in response to changes to the parameters (3 \& 4).

>>>>

\begin{table}[h!]
\center
\begin{tabular} {|l | l | c|}
\hline
Name & Description & Value \\ \hline
\(n_{w}\) & Number of women & 1000 \\ \hline
\(n_{m}\) & Number of midwives & 100 \\ \hline
\(r_{m}\) & Number of appointments per midwife & 1000 \\ \hline
\(r_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
Runs & Simulation runs & 1000 \\ \hline
\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(q_{w}\) & Probability of women sharing & 0. \\ \hline
\(w_{w}\) & Weight of shared information for women & 0. \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 10:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}

@@

Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of inputs given in table \ref{tab:sa_params}, giving 10 free parameters which were treated as uniformly distrubuted in the range given. Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters. Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out cross validation. A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.

To capture the response characteristics for the model, we measure four outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the interquartile range of the average signal, and interquartile range between simulation runs. Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability in the system in response to changes to the parameters (3 \& 4).

### 2014-08-30 SensitivityAnalysis.tex
Wrong brackets
Fixed number of columns
Tables, switched to input rather than include
Because nesting

\subsubsection{Median Moderate Drinker Signalling}

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1.145 & 0.801 & 0.614 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 37.750 & 23.968  & 5.137\\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 13.017 & 0.894 & 1.485\\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1.655 & 1.602 & 2.618 \\ \hline
\(q_{w}\) & Probability of women sharing & 0.198 & 5.527 & 4.460 & 1.159 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0.355 & 13.025 & 2.716 & 0.888 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0.145 & 0.667 & 0.368 & 0.157 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0.118 & 0.376 & 0.176 & 0.200 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 9.618 & 1.912 & 15.355 \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.140 & 7.537 & 10.427 & 7.795 \\ \hline
\end{tabular}
\caption[Table caption text]{Median moderate drinker signalling parameter sensitivity. \label{tab:sa_results_sig}}
\end{table}

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
Bayesian Payoff & 1.667 & 0.475 &  0.662 & 0.003 & 0.181 & 3.12 \\ \hline
Bayesian & 3.352 & 0.534 & 1.160 & 0.001 & 0.068 & 2.423 \\ \hline
\ac{CPT} & 1.503 & 0.331 & 1.241 & 0.002 & 0.101 & 1.842 \\ \hline
\end{tabular}
\caption[Table caption text]{Median moderate drinker signalling emulator statistics. \label{tab:sa_emulator_sig}}
\end{table}

\subsubsection{Median Between Groups IQR}

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.327 & 0.688 & 0.457 & 0.586 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 11.223 & 20.123 & 11.046 & 4.081 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 36.630 & 1.160 & 0.364 & 1.945 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 6.228 & 4.487 & 0.0964 & 2.627\\ \hline
\(q_{w}\) & Probability of women sharing & 0.498 & 0.235 & 2.537 & 1.812 \\ \hline
\(w_{w}\) & Weight of shared information for women & 1.018 & 2.307 & 1.889 & 0.740 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0.158 & 0.343 & 0.387 & 0.156 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0.076 & 0.973 & 0.125 & 0.213 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 0.317 & 10.960 & 3.305 & 16.493 \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1.107 & 8.411 & 2.890 & 6.729 \\ \hline
\end{tabular}
\caption[Table caption text]{Median between groups IQR parameter sensitivity. \label{tab:sa_results_iqr}}
\end{table}

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
Lexicographic & 0.930 & 0.240 & 0.249 & 0.002 & 0.040 & 1.832 \\ \hline
Bayesian Payoff & 1.242 & 0.417 & 0.232 & 0.001 & 0.0034 & 2.308 \\ \hline
Bayesian & 1.254 & 0.131 & 0.644 & 0.000 & 0.019 & 1.167 \\ \hline
\ac{CPT} & 1.190 & 0.313 & 0.659 & 0.000 & 0.024 & 1.701 \\ \hline
\end{tabular}
\caption[Table caption text]{Median between groups IQR emulator statistics. \label{tab:sa_emulator_iqr}}
\end{table}

\subsubsection{Median Moderate Drinker Signalling IQR}

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.428 & 9.828 & 3.816 & 2.068 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 8.369 & 13.791 & 4.045 & 2.400 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 13.416 & 0.712 & 0.676 & 0.583 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 21.079 & 0.648 & 0.659 & 0.373 \\ \hline
\(q_{w}\) & Probability of women sharing & 2.307 & 3.481 & 0.891 & 0.600 \\ \hline
\(w_{w}\) & Weight of shared information for women & 6.021 & 6.009 & 0.562 & 0.937 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0.315 & 1.829 & 0.114 & 0.117 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 1.652 & 1.354 & 0.260 & 0.0.139 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 0.253 & 0.612 & 4.889 & 15.146 \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.504 & 3.096 & 19.863 & 25.999 \\ \hline
\end{tabular}
\caption[Table caption text]{IQR of median moderate drinker signalling parameter sensitivity. \label{tab:sa_results_sig_iqr}}
\end{table}

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
Lexicographic & 1.425 & 0.436 & 0.549 & 0.008 & 0.114 & 2.719 \\ \hline
Bayesian Payoff & 1.223 & 0.496 & 0.747 & 0.012 & 0.207 & 2.034 \\ \hline
Bayesian &  1.065 & 0.000 & 0.230 & 0.002 & 0.088 & 1.015 \\ \hline
\ac{CPT} & 0.874 & 0.213 & 0.233 & 0.001 & 0.066 & 1.806 \\ \hline
\end{tabular}
\caption[Table caption text]{IQR of median between groups IQR emulator statistics. \label{tab:sa_emulator_sig_iqr}}
\end{table}

\subsubsection{Between Groups IQR IQR}

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.691 & 5.926 & 1.053 & 1.265 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 3.664 & 17.047 & 4.877 & 3.656 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 41.369 & 1.124 & 0.814 & 0.591 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 7.109 & 0.739 & 0.496 & 0.378 \\ \hline
\(q_{w}\) & Probability of women sharing & 1.963 & 2.038 & 0.733 & 0.589 \\ \hline
\(w_{w}\) & Weight of shared information for women & 7.932 & 11.193 & 2.289 & 1.960 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0.413 & 1.972 & 0.267 & 0.069\\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0.120 & 2.902 & 0.150 & 0.123 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 0.228 & 3.190 & 6.308 & 14.777 \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.673 & 10.411 & 22.901 & 26.340 \\ \hline
\end{tabular}
\caption[Table caption text]{IQR of median between groups IQR parameter sensitivity. \label{tab:sa_results_iqr_iqr}}
\end{table}

\begin{table}[h!]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
Lexicographic & 0.826 & 0.409 & 0.259 & 0.002 & 0.034 & 2.364 \\ \hline
Bayesian Payoff & 3.202 & 0.520 & 0.328 & 0.002 & 0.032 & 2.452 \\ \hline
Bayesian & 1.177 & 0.041 & 0.133 & 0.000 & 0.018 & 1.152 \\ \hline
\ac{CPT} & 0.874 & 0.118 & 0.126 & 0.000 & 0.017 & 1.570 \\ \hline
\end{tabular}
\caption[Table caption text]{IQR of median between groups IQR emulator statistics. \label{tab:sa_emulator_iqr_iqr}}
\end{table}

>>>>

\subsection{Median Moderate Drinker Signalling}

\begin{table}[H]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1.145 & 0.801 & 0.614 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 37.750 & 23.968  & 5.137\\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 13.017 & 0.894 & 1.485\\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1.655 & 1.602 & 2.618 \\ \hline
\(q_{w}\) & Probability of women sharing & 0.198 & 5.527 & 4.460 & 1.159 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0.355 & 13.025 & 2.716 & 0.888 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0.145 & 0.667 & 0.368 & 0.157 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0.118 & 0.376 & 0.176 & 0.200 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 9.618 & 1.912 & 15.355 \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.140 & 7.537 & 10.427 & 7.795 \\ \hline
Total & All parameters and two way interactions & 86.777 & 96.527 & 85.529 & 74.123 \\ \hline
\end{tabular}
\caption[Table caption text]{Median moderate drinker signalling parameter sensitivity. \label{tab:sa_results_sig}}
\end{table}

\begin{table}[H]
\center
\begin{tabular} {|l | l | l | l | l | l | l |}
\hline
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
Bayesian Payoff & 1.667 & 0.475 &  0.662 & 0.003 & 0.181 & 3.12 \\ \hline
Bayesian & 3.352 & 0.534 & 1.160 & 0.001 & 0.068 & 2.423 \\ \hline
\ac{CPT} & 1.503 & 0.331 & 1.241 & 0.002 & 0.101 & 1.842 \\ \hline
\end{tabular}
\caption[Table caption text]{Median moderate drinker signalling emulator statistics. \label{tab:sa_emulator_sig}}
\end{table}

\input{top_5_table_sig}

\subsection{Median Between Groups IQR}

\begin{table}[H]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.327 & 0.688 & 0.457 & 0.586 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 11.223 & 20.123 & 11.046 & 4.081 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 36.630 & 1.160 & 0.364 & 1.945 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 6.228 & 4.487 & 0.0964 & 2.627\\ \hline
\(q_{w}\) & Probability of women sharing & 0.498 & 0.235 & 2.537 & 1.812 \\ \hline
\(w_{w}\) & Weight of shared information for women & 1.018 & 2.307 & 1.889 & 0.740 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0.158 & 0.343 & 0.387 & 0.156 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0.076 & 0.973 & 0.125 & 0.213 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 0.317 & 10.960 & 3.305 & 16.493 \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1.107 & 8.411 & 2.890 & 6.729 \\ \hline
Total & All parameters and two way interactions & 81.702 & 83.693 & 47.449 & 71.032 \\ \hline
\end{tabular}
\caption[Table caption text]{Median between groups IQR parameter sensitivity. \label{tab:sa_results_iqr}}
\end{table}

\begin{table}[H]
\center
\begin{tabular} {|l | l | l | l | l | l | l |}
\hline
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
Lexicographic & 0.930 & 0.240 & 0.249 & 0.002 & 0.040 & 1.832 \\ \hline
Bayesian Payoff & 1.242 & 0.417 & 0.232 & 0.001 & 0.0034 & 2.308 \\ \hline
Bayesian & 1.254 & 0.131 & 0.644 & 0.000 & 0.019 & 1.167 \\ \hline
\ac{CPT} & 1.190 & 0.313 & 0.659 & 0.000 & 0.024 & 1.701 \\ \hline
\end{tabular}
\caption[Table caption text]{Median between groups IQR emulator statistics. \label{tab:sa_emulator_iqr}}
\end{table}

\input{top_5_table_group_iqr}

\subsection{Median Moderate Drinker Signalling IQR}

\begin{table}[H]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.428 & 9.828 & 3.816 & 2.068 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 8.369 & 13.791 & 4.045 & 2.400 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 13.416 & 0.712 & 0.676 & 0.583 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 21.079 & 0.648 & 0.659 & 0.373 \\ \hline
\(q_{w}\) & Probability of women sharing & 2.307 & 3.481 & 0.891 & 0.600 \\ \hline
\(w_{w}\) & Weight of shared information for women & 6.021 & 6.009 & 0.562 & 0.937 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0.315 & 1.829 & 0.114 & 0.117 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 1.652 & 1.354 & 0.260 & 0.0.139 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 0.253 & 0.612 & 4.889 & 15.146 \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.504 & 3.096 & 19.863 & 25.999 \\ \hline
Total & All parameters and two way interactions & 84.9968 & 77.413 & 57.125 & 83.322 \\ \hline
\end{tabular}
\caption[Table caption text]{IQR of median moderate drinker signalling parameter sensitivity. \label{tab:sa_results_sig_iqr}}
\end{table}

\begin{table}[H]
\center
\begin{tabular} {|l | l | l | l | l | l | l |}
\hline
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
Lexicographic & 1.425 & 0.436 & 0.549 & 0.008 & 0.114 & 2.719 \\ \hline
Bayesian Payoff & 1.223 & 0.496 & 0.747 & 0.012 & 0.207 & 2.034 \\ \hline
Bayesian &  1.065 & 0.000 & 0.230 & 0.002 & 0.088 & 1.015 \\ \hline
\ac{CPT} & 0.874 & 0.213 & 0.233 & 0.001 & 0.066 & 1.806 \\ \hline
\end{tabular}
\caption[Table caption text]{IQR of median between groups IQR emulator statistics. \label{tab:sa_emulator_sig_iqr}}
\end{table}

\input{top_5_table_sig_iqr}

\subsection{Between Groups IQR IQR}

\begin{table}[H]
\center
\begin{tabular} {|l | l | l | l | l | l |}
\hline
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.691 & 5.926 & 1.053 & 1.265 \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & 3.664 & 17.047 & 4.877 & 3.656 \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & 41.369 & 1.124 & 0.814 & 0.591 \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 7.109 & 0.739 & 0.496 & 0.378 \\ \hline
\(q_{w}\) & Probability of women sharing & 1.963 & 2.038 & 0.733 & 0.589 \\ \hline
\(w_{w}\) & Weight of shared information for women & 7.932 & 11.193 & 2.289 & 1.960 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0.413 & 1.972 & 0.267 & 0.069\\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0.120 & 2.902 & 0.150 & 0.123 \\ \hline
\(x_{h}\) & Health payoff for healthy delivery & 0.228 & 3.190 & 6.308 & 14.777 \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.673 & 10.411 & 22.901 & 26.340 \\ \hline
Total & All parameters and two way interactions & 85.740 & 88.611 & 68.640 & 84.210 \\ \hline
\end{tabular}
\caption[Table caption text]{IQR of median between groups IQR parameter sensitivity. \label{tab:sa_results_iqr_iqr}}
\end{table}

\begin{table}[H]
\center
\begin{tabular} {|l | l | l | l | l | l | l |}
\hline
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
Lexicographic & 0.826 & 0.409 & 0.259 & 0.002 & 0.034 & 2.364 \\ \hline
Bayesian Payoff & 3.202 & 0.520 & 0.328 & 0.002 & 0.032 & 2.452 \\ \hline
Bayesian & 1.177 & 0.041 & 0.133 & 0.000 & 0.018 & 1.152 \\ \hline
\ac{CPT} & 0.874 & 0.118 & 0.126 & 0.000 & 0.017 & 1.570 \\ \hline
\end{tabular}
\caption[Table caption text]{IQR of median between groups IQR emulator statistics. \label{tab:sa_emulator_iqr_iqr}}
\end{table}

\input{top_5_table_group_iqr_iqr}
